%!TEX root=../main.tex

% Notes Whiteboard:
%
% 3 Motivation and Goals (Design Goals)
% 3.1 Problem with current BMS Metadata
% - misspelling
% - missing
%
% Design Goals:
%
% - existing buildings (policy, technical BMS, bacnet)
% - crwoudsourcable
% - incremental
% - robustness of structure 100\%

\section{Motivation and Design Goals} % (fold) 
\label{sec:motivation_and_design_goals}

\subsection{Analyis of Current BMS State} % (fold)
\label{sub:analyis_of_current_bms_state}
\fixme{I think we need a more detailed problem statement before the architecture section, maybe it is a section itself. basically it should talk about problems in current building metadata, and why a clean metada is soooo important to applications. it should be driven by real data/metadata. we can grab some from sMAP archiver.  -Kaifei}

\fixme{I aggree  --Jonathan}

\begin{enumerate}

  \item What systems are used?

  \item How do they do naming? (with example using the berkeley data set)

  \item Why is this (which might not have been such a big poblem before) now a problem if we want to allow smart applications for users?

\end{enumerate}


% subsection analyis_of_current_bms_state (end)

\subsection{Design Goals} % (fold)
\label{sub:design_goals}
\fixme{
Maybe we should have a more sophisticated, stepwise system.
Use matching/linking by users to learn types
For example, if we know 5 lights, we might be able to tell which points the other lights are.
This should be realtively simple.
It would be cool to investigate if we can do the same for the structural relationship.
Can we learn which things are in the same room by looking at the existing metadata in the BMS.
We probably can, but depends if this goes against the initial assumption to not consider the metadata of the BMS.
Still there must be some structure in it that will be useful. --Jonathan
}

\fixme{We need to think about the structural model of a building. We have two choices: (i) a structural model exists and our application uses it. E.g. All rooms, floors etc are already somewhere on the server and our application queries it and show the user a list. (ii) we let the user enter things, probbaly following some schema (e.g., a room always needs a number and a floor.)
Problem is not all rooms might have numbers like we said.  --Jonathan}

% subsection design_goals (end)

% section motivation_and_design_goals (end)